### 2025-07-09 getting-started.qmd
20250709 - consolidate packages using package ecosystems

   install.packages(
     c("petersenlab","remotes","knitr","rmarkdown","dplyr",
       "ggplot2","tidyverse","psych","xfun","downlit","xml2",
       "nflreadr","nflplotR","nflfastR","nflseedR","nfl4th",
       "gsisdecoder","progressr","DescTools","pwr","pwrss",
       "WebPower","XICOR","dagitty","ggdag","lubridate",
       "ggtext","gghighlight","ggExtra","grid","patchwork",
       "pROC","lme4","lmerTest","MuMIn","emmeans","pbkrtest",
       "sjstats","AICcmodavg","rstan","brms","bbmle",
       "fitdistrplus","mclust","magrittr","viridis","viridisLite",
       "msir","plotly","webshot2","quantmod","fPortfolio",
       "xts","zoo","forecast","stringi","parallel","parallelly",
       "doParallel","missRanger","powerjoin","caret","gpboost",
       "ggridges","corrplot","rms","car","caret","performance",
       "correlation","interactions","lavaan","mice","miceadds",
       "robustbase","see"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

>>>>

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","grid","patchwork",
     "pROC", "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats",
     "AICcmodavg","rstan","brms","tidybayes","bbmle","fitdistrplus","sn",
     "mclust","magrittr","viridis","viridisLite","msir","plotly","webshot2",
     "quantmod","fPortfolio","NMOF","nFactors","xts","zoo","forecast","stringi",
     "parallelly","doParallel","missRanger","ggridges","powerjoin","caret",
     "LongituRF","gpboost","corrplot","mgcv","rms","car","lavaan","lavaangui",
     "mice","miceadds","interactions","robustbase","ordinal","MASS",
     "data.table","future","future.apply","SimDesign"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

### 2025-07-09 index.qmd
20250709 - consolidate packages using package ecosystems

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast", "stringi", #"webshot2"
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", 
  "remotes", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "lavaangui", "mice", "miceadds", "interactions", "shiny", 
  "PearsonDS", "robustbase", "ordinal", "MASS", "data.table", "future", 
  "future.apply", "QuantPsyc", "SimDesign", "effectsize"
)

>>>>

# Packages to drop: stringi (replace with stringr from tidyverse); caret (replace with tidymodels)

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "stringi", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "LongituRF", "gpboost", "cmdstanr", "corrplot", "mgcv", "rms", 
  "car", "lavaan", "lavaangui", "mice", "miceadds", "interactions", 
  "robustbase", "ordinal", "MASS", "data.table", "future", "future.apply", 
  "SimDesign",
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)
